\chapter{Gossamer}
\label{gossamer}

Delegation has a programming model that works very well for distributed computing. Like distributed systems, 
delegation does not have to rely on shared memory for operations. This makes it possible to write an 
application that is designed for a single machine delegated system and then adapt it for a distributed 
delegation system without significant changes to application code.
  
We introduce \name{}, a distributed programming model that leverages delegation to efficiently distribute 
computation across machines. \name{} uses Remote Direct Memory Access (RDMA) for inter-node communication, 
offering low latency, high throughput, and direct remote memory access without CPU involvement. This enables a 
unified programming abstraction that functions seamlessly on both single and multi-machine setups.
  
With \name{}, developers can write distributed applications as if they were running on a single system. Its API 
allows delegation of Rust closures for remote execution, and lightweight user-space threads (\textit{fibers}) provide 
efficient concurrency. Experimental results show that Gossamer achieves up to 3x higher throughput scaling than 
eRPC in microbenchmarks and matches the performance of the Graph500 reference implementation of single-source 
shortest path (SSSP) using MPI.

% \setcounter{table}{0}
\input{sections/4_Gossamer/intro}
\input{sections/4_Gossamer/1_rdma}
\input{sections/4_Gossamer/2_Gossamer_Design}
\input{sections/4_Gossamer/3_eval}
\input{sections/4_Gossamer/conclusion}
