\chapter{Gossamer}
\label{gossamer}

Delegation has a programming model that works very well for distributed computing. Like distributed systems, 
delegation does not have to rely on shared memory for operations. This makes it possible to write an 
application that is designed for a single machine delegated system and then adapt it for a distributed 
delegation system without significant changes to application code.
  
We describe the design and implementation of \name{}, a new distributed programming model that uses delegation 
to distribute computing work. We use RDMA for communication between machines as it provides both low latency 
and high throughput. Moreover, RDMA offers mechanism to write in a remote machine's memory without the 
involvement of CPU on that machine. This is especially useful when implementing a programming model that can 
seamlessly work on both a single machine and multiple machines.
  
\name{} allows developers to write applications that span multiple machines as if they would be running on a 
single machine. Programmers can use the API provided by \name{} to delegate a rust closure that can even be 
executed on a remote machine. \name{} uses light weight user-space threads called \textit{fibers} for 
multi-threading on both machines. In our evaluation, we compare the performance of applications running 
delegation over RDMA that of applications running on a single machine, while using the same number of CPUs.

% \setcounter{table}{0}
\input{sections/3_Gossamer/1_rdma}
\input{sections/3_Gossamer/2_Gossamer_Design}
\input{sections/3_Gossamer/3_plots}
