\chapter*{Acknowledgements}

I am deeply grateful to many individuals who have helped me along this journey.

First, I would like to thank my advisor, Dr. Jakob Eriksson, for his clear guidance, remarkable patience and 
unwavering support. He taught me how to think like a researcher and approach problems in computer systems. He 
always made me feel smart during our conversations and encouraged me to follow my heart. Without him, this 
dissertation would not be possible.

I would also like to thank Dr. Brent Stephens for his help and insights during my first two years at UIC. His 
presence during our weekly meetings during that time had been very reassuring, and I'll always appreciate that 
early support.

In addition, I would like to extend my gratitude to the member of my defense committee. Dr. Erdem Koyuncu, Dr. 
Lu\'{i}s Pina, Dr. Ajay Kshemkalyani, Dr. Michael Papka, and Dr. Xingbo Wu have all been very helpful and 
understanding. Their diverse perspective has been invaluable for this work.

I am extremely grateful to Dr. Junaid Haroon Siddiqui and Dr. Fareed Zaffar for their guidance during undergrad 
and their encouragement to pursue higher studies.

My thanks also go to the members of my research group including Ben Baenen, Dr. Nilanjana Basu, Dr. Chen Chen, 
and Jacob Cohen for the many conversations, both intellectual and casual, that helped me grow as a person and a 
scientist.

I am thankful to Ahsen Ghafoor, Taha Moaz, Dr. Ahmed Akhtar, Umar pervaiz, Danyal Saeed, and Dr. Usama Muneeb, 
for their friendship, the casual conversations, the jokes and also the help whenever I needed them.

Finally, I am grateful for the love and support of my family, who have helped me at every step of my journey. 
From the sacrifices of my parents to the emotional support of my siblings, and to my aunt and uncle who welcomed 
me into their home every year since I arrived in the U.S., I cannot express how much it all means to me. I will 
cherish it for the rest of my life.

% This line is required, but of course replace my initials with yours.
\initials{NA}